---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
```{r load-data,echo=FALSE}
data(jobs)
```

[![Travis-CI Build Status](https://travis-ci.org/jaredlander/resumer.svg?branch=master)](https://travis-ci.org/jaredlander/resumer)
[![Coverage Status](https://img.shields.io/codecov/c/github/jaredlander/resumer/master.svg)](https://codecov.io/github/jaredlander/resumer?branch=master)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/resumer)](http://cran.r-project.org/package=resumer)

# resumer

This package stores information for your CV in a CSV and compiles a nicely formatted LaTeX CV.

## Data
Your jobs should be stored in a CSV with these names:  `r names(jobs)`.

An example file can be found in [`inst/examples/Jobs.csv`](https://github.com/jaredlander/resumer/blob/master/inst/examples/Jobs.csv) or by running

```{r show-jobs,eval=FALSE}
data(jobs)
head(jobs)
```

```{r show-jobs-do,echo=FALSE}
knitr::kable(head(jobs))
```



## Usage
In order to make this package as universal as possible it is designed for some information to be input in the yaml header and some in R code.  Creating a new file using the template through RStudio will be easiest.

### yaml header
Here you put your name, address, the location of the jobs CSV, education information and any highlights.

## Resources

### LaTeX Templates
- https://www.sharelatex.com/blog/2011/03/27/how-to-write-a-latex-class-file-and-design-your-own-cv.html

### Pandoc
- http://pandoc.org/scripting.html
- http://pandoc.org/README.html#header-identifiers-in-html-latex-and-context
- https://github.com/jgm/pandocfilters/blob/master/pandocfilters.py
- http://galahad.well.ox.ac.uk/repro/#latex-output
